---
title: "Machine Learning Project"
author: "Nathan E. Wendling"
date: "December 27, 2015"
output: html_document
---

*Preprocessing:*
Before the file could hit R, I went in with a text editor and manually removed all the doublequotes from the file as the file was not going through read.table properly.  Find-replace'd all \"s with nothing (not even a space) given that there were over 300,000 double quotes, I suppose it isn't all that unlikely for a data entry error to crop up.'

*Import:*
```{r init, eval=FALSE}
library(caret)
training <- read.csv("pml-training.csv",na.strings=c("NA",""))
testing <-read.csv("pml-testing.csv",na.strings=c("NA",""))
```

*Imputing:*
With the proponderance of NA values in the dataset, a good number of the columns were outright ignored as not useful for prediction.  The raw timestamp (both halves) was used instead of the human readable version.

Thus we use 
```{r nanana, eval=FALSE}
uselesscol <- colSums(is.na(training))
newTraining <- training[,!(uselesscol > 100)]   
uselessrow <- rowSums(is.na(training))
newTraining <- training[!(uselessrow > 0)]   #strict
```